---
title: "Developing Data Product Week 2 Project"
author: "Sunil Samson S"
date: "10/18/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="#/>")
```


## Overview 
The aim of this project is to create a web page using R Markdown that contains a map made with leaflet pakage which shows cities with highest population in India.

## Source of Information 
A part of the data was collected from wikipedia and the latitude & longitude data was taken from Google Maps.

## Installing the packages
```{r}
#install.packages("leaflet") This is a comment as the package is already installed.
```

## Cities with highest population in India.
#### Adding Markers
```{r}
library(leaflet)
my_map <- leaflet() %>% addTiles()

my_map <- my_map %>%
addMarkers(lat=17.387140, lng=78.491684, popup = "Hyderabad, India")

my_map <- my_map %>%
  addMarkers(lat=18.987807, lng=72.836447, popup = "Mumbai, India")

my_map <- my_map %>%
addMarkers(lat=	22.562627, lng=	88.363044, popup = "Kolkata, India") 

my_map <- my_map %>%
  addMarkers(lat=13.084622, lng= 80.248357, popup = "Chennai, India")

my_map <- my_map %>%
addMarkers(lat=12.977063, lng=	77.587106, popup = "Bengaluru, India")  

my_map <- my_map %>%
addMarkers(lat=28.651952, lng=	77.231495, popup = "Delhi, India")


my_map
```


